Heavy Rainfall in Paraguay During the 2015-2016 Austral Summer: Causes and Sub-Seasonal-to-Seasonal Predictive Skill

### 2018-09-12 reports/poster/blocks/mjo-enso.tex
excise princeton and fix erroneous cref

\begin{block}{ENSO, MJO, and Weather Types}
    \begin{framed}
        \begin{figure}
            \centering
            \caption{
                Anomalous probability of occurrence of each weather type concurrent with observance of each MJO and ENSO phase.
                Only values which are significant at $p < 0.10$ are shown.
            }\label{fig:wt-mjo-ensoflooded}
            \includegraphics[width=\textwidth]{wt_mjo_enso.pdf}
        \end{figure}
    \end{framed}
    \gls{wt} 1 occurs more frequently during El Ni\~{n}o years for most \gls{mjo} phases, particularly during phase 2.
    During El Ni\~no years, \gls{wt} 3 - associated with dryness over the \gls{lprb} - occurs less frequently during \gls{mjo} phases 4, 6, and 7, and more often during \gls{mjo} phase 8; this is consistent with the lack of \gls{wt} 3 during December 2015 and the frequent \gls{wt} 3 occurrence in mid-January 2016 (\cref{fig:fig:rain-wtype}).
\end{block}

>>>>

\begin{block}{ENSO, MJO, and Weather Types}
    \begin{framed}
        \begin{figure}
            \centering
            \caption{
                Anomalous probability of occurrence of each weather type concurrent with observance of each MJO and ENSO phase.
                Only values which are significant at $p < 0.10$ are shown.
            }\label{fig:wt-mjo-ensoflooded}
            \includegraphics[width=\textwidth]{wt_mjo_enso.pdf}
        \end{figure}
    \end{framed}
    \gls{wt} 1 occurs more frequently during El Ni\~{n}o years for most \gls{mjo} phases, particularly during phase 2.
    During El Ni\~no years, \gls{wt} 3 - associated with dryness over the \gls{lprb} - occurs less frequently during \gls{mjo} phases 4, 6, and 7, and more often during \gls{mjo} phase 8; this is consistent with the lack of \gls{wt} 3 during December 2015 and the frequent \gls{wt} 3 occurrence in mid-January 2016 (\cref{fig:rain-wtype}).
\end{block}

### 2018-09-12 reports/poster/poster.tex
excise princeton and fix erroneous cref

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Doss-Gollin, J., Á. G. Muñoz, S. J. Mason, and M. Pastén (2018), Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill, Journal of Climate, doi:\href{dx.doi.org/10.1175/JCLI-D-17-0805.1}{10.1175/JCLI-D-17-0805.1}.}
\newcommand{\footright}{}
\title{Heavy Rainfall in Paraguay During the 2015-2016 Austral Summer: Causes and Sub-Seasonal-to-Seasonal Predictive Skill}
\author{James Doss-Gollin\inst{1} \quad \'{A}ngel G. Mu\~{n}oz\inst{2,3} \quad Simon J. Mason\inst{3} \quad Max Past\'{e}n\inst{4}}
\institute
{\inst{1} Columbia Water Center, Columbia University \inst{2} AOS, Princeton University \inst{3} International Research Institute for Climate and Society, Columbia University \inst{4} Direcci\'{o}n de Meteorolog\'{i}a e Hidrolog\'{i}a, Paraguay}

>>>>

%-- Header and footer information ----------------------------------
\newcommand{\footleft}{Doss-Gollin, J., Á. G. Muñoz, S. J. Mason, and M. Pastén (2018), Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill, Journal of Climate, doi:\href{dx.doi.org/10.1175/JCLI-D-17-0805.1}{10.1175/JCLI-D-17-0805.1}.}
\newcommand{\footright}{}
\title{Heavy Rainfall in Paraguay During the 2015-2016 Austral Summer: Causes and Sub-Seasonal-to-Seasonal Predictive Skill}
\author{James Doss-Gollin\inst{1} \quad \'{A}ngel G. Mu\~{n}oz\inst{2} \quad Simon J. Mason\inst{2} \quad Max Past\'{e}n\inst{3}}
\institute
{\inst{1} Columbia Water Center, Columbia University \inst{2} International Research Institute for Climate and Society, Columbia University \inst{3} Direcci\'{o}n de Meteorolog\'{i}a e Hidrolog\'{i}a, Paraguay}
